### 2024-01-29 README.Rmd
update readme

@@

1.  Process and tabulate the annotations. TODO: first local then containerized

```{r}

```

>>>>

## Processing detections

<!-- 1.  Process and tabulate the annotations. -->

```{r, eval=FALSE}
detections <- rofcamtrap::process_detections(
  input_dir = "2_LabelStudio/0_inputs/")
saveRDS(detections, "data/objects/detections.rds")
```

@@

1.  Process and tabulate the annotations.

```{r, eval=FALSE}
annotations <- rofcamtrap::process_annotations(
   input_dir = "2_LabelStudio/2_outputs_processed/")

saveRDS(annotations, "data/objects/annotations_wide_treated.rds")

# Filter for non empty images
annotations_noempty <- annotations |>
  dplyr::filter(!is.na(to_name))

saveRDS(annotations_noempty, "data/objects/annotations_wide_noempty.rds")
```
